Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-11-15 lloveras_2020.tex
agregado de plots de perfiles radiales de ne y te

@@

>>>>

\begin{figure}%[h]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_cr2082_ne.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_cr2082_te.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_cr2208_ne.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_cr2208_te.eps}
\caption{Latitude-longitude location of field lines meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082(left panel) and CR-2208 (right panel). Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
\label{rpoint}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_lowlat_ncb.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_midlat_S_ncb.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_lowlat_lambda.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_midlat_S_lambda.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_lowlat_tm.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_midlat_S_tm.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_lowlat_bcb.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_midlat_S_bcb.pdf}
\caption{
{Comparative statistical distributions of (from top to bottom): the coronal base electron density $\NCB\equiv N_e(r=1.025\,\mrsun)$, the electron density scale height $\lN$, the average electron mean temperature $\aTm$, and the coronal base magnetic field strength $B_{\rm CB}$, along all field lines traced in the low-latitudes of the equatorial streamer (region ES-Ll, left panels) and the southern mid-latitudes of the equatorial streamer (region ES-Sm, right panels), for CR-2081 (solid-blue) and CR-1915 (dashed-red). In each panel the median $m$, mean $\mu$, fractional standard deviation $\sigma/\mu$, and number of traced loops $N$, are indicated.}
}
\label{compES}
\end{center}
\end{figure}

For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}. For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}. As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}T_m/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$. Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_L_ncb.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_H_ncb.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_L_lambda.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_H_lambda.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_L_tm.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_H_tm.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_L_bcb.pdf}
\includegraphics[width=0.495\textwidth,clip=]{test_comp_open_S_H_bcb.pdf}
\caption{Same as Figure \ref{compES} but for all field lines traced in the low-latitudes of the southern coronal hole (region CH-Sl, left panels) and the high-latitudes of the southern coronal hole (region CH-Sh, right panels).}
\label{compCH}
\end{center}
\end{figure}
